The low-frequency environment of the Murchison Widefield Array: radio-frequency interference analysis and mitigation

### 2014-11-25 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Small details

\ifpdf\pdfinfo{/Title      (Analysis of the Murchison radio environment for low-frequency astronomy)
               /Author     (A. R. Offringa et al.)
               /Keywords   (instrumentation: interferometers;methods: observational;techniques: interferometric;radio continuum: general)
        }
\else\usepackage{graphics}\fi
\usepackage{graphics}

@@

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/lognlogs-multiplot}
\caption{Visibility amplitude distributions with logarithmic axes. The dashed line represent fits to the function $N=\beta S^\alpha$ over a reasonably constant part of the tail (selected by eye) of the RFI distribution, resulting in $\alpha=-1.37$ for GLEAM, $\alpha=-4.47$ for EoR high, and $\alpha=-1.33$ for EoR low.}
\label{fig:lognlogs}
\end{center}
\end{figure*}

>>>>

\ifpdf\pdfinfo{/Title      (The low-frequency environment of the Murchison Widefield Array: radio-frequency interference analysis and mitigation)
               /Author     (A. R. Offringa et al.)
               /Keywords   (instrumentation: interferometers;methods: observational;techniques: interferometric;radio continuum: general)
        }
\else\usepackage{graphics}\fi
\usepackage{graphics}

@@

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/lognlogs-multiplot}
\caption{Visibility amplitude distributions with logarithmic axes. The dashed line represent fits to the function $N=\beta S^\alpha$ over a reasonably constant part of the tail (gray area, selected by eye) of the RFI distribution, resulting in $\alpha=-1.37$ for GLEAM, $\alpha=-4.47$ for EoR high, and $\alpha=-1.33$ for EoR low.}
\label{fig:lognlogs}
\end{center}
\end{figure*}
